---
output:
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview

`"binomial"` binomial is a package that implement functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distriburion, the expected value, variance, etc.

* `bin_variable()` creates a binomial random variable object (of class `"binvar"`)
* `bin_distribution()` create a object of `"bindis"` class and ouput a table that display the probability distriburion.
* `bin_cumulative()` create a object of `"bincum"` class and ouput a table that display the probability distribution
* `plot()` method for `"bindis"` and `"bincum"` objects to plot the probability distriburion histogram and cumulative probability distribution plot.
* `summary()` method for a `"binvar"` object.
* `bin_mean()`: calculate the mean of the binomial random variable
* `bin_variance()`: calculate the variance of the binomial random variable
* `bin_mode()`: calculate the mode of the binomial random variable
* `bin_skewness()`: calculate the skewness of the binomial random variable
* `bin_kurtosis()`: calculate the kurtosis of the binomial random variable


## Motivation

This package has been developed to illustrate some of the concepts behind the creation of an R package.


## Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
#install.packages("devtools") 
# install "binomial" (without vignettes)
devtools::install_github("eden98lin/binomial")
# install "binomial" (with vignettes)
devtools::install_github("eden98lin/binomial", build_vignettes = TRUE)
```


## Usage

```{r}
library(binomial)
# a binomial random variable with n = 5, p = 0.2
rand_var <- bin_variable(5, 0.2)
rand_var
# summary of measures of the binomial random variable
bin_sum <- summary(rand_var)
bin_sum
# binomial probability distribution and binomial cumulative probability distribution
dist1 <- bin_distribution(5, 0.2)
dist1
dist2 <- bin_cumulative(5, 0.2)
dist2
# plot
plot(dist1)
plot(dist2)
```
